Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-27 ms.tex
added more description of the high resolution spectra.

The 2013 HDS data for KIC 1255 display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas

@@

\section{Conclusions}\label{sec:conclusions}

>>>>

The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.

After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the Mg Triplet (Figure \ref{fig:mgTriplet}).
The Mg triplet is diagnostic of spectral type and may help resolve some of the conflicts in the literature about the gravity of the host star.
\citet{kawahara2013starspots} find a log(g) = 3.9 $\pm$ 0.2, whereas \citet{rappaport} find a log(g)=4.63.
To compare to some HIGHRES models \citep{coelho2014hires}, we first had to convolve the spectrum.
Also, we interpolated over any pixels above a normalized flux of 2.0 in Figure \ref{fig:mgTriplet} (top).
Then, we convolve with a Gaussian kernel with a standard deviation of 6 pixels.

@@

\clearpage
\section{Conclusions}\label{sec:conclusions}
